### 2016-03-31 paper.tex
add new picture and data volume

		\section{Estimation of data volume in JUNO}
		JUNO is proposed to run at least 6 years for neutrino mass hiarachy measurements and other physics topics. 
		It's important for offline data processing and disk storage preparation to estimate the data volume after 6 years running. 
		Different events have different event size, depending on number of photo-electrons detected by CD.
		The data volume of physical events excepting muon events and supernova events can be negligible comparing with radioactivity events. 
		Fig.5  shows the fired PMT number distributions from different radioactivity events on each detector material.

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{distribution_of_fired_PMTNum.eps}
			\figcaption{\label{fig2}   Distributions of fired PMT number on different materials}
		\end{center}

@@

		In JUNO electronic system for low energy radioactivity events the assuming sampling time window is 1 $\mu$s. Each sampling point contribute 2 bytes data, so each low energy event contribute 2 MBytes data. The estimated data volume about radioactivity events of CD on different energy and radius threshold is listed in table 6.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The data volume of central detector radioactivity events on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  disk storage space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m  &122.630  &118.468  &118.362  &118.257  &118.159  &118.051 \\  
			R$<$11m  &123.806  &118.554  &118.429  &118.309  &118.201  &118.062 \\
			R$<$12m  &128.531  &118.897  &118.697  &118.523  &118.371  &118.104 \\
			R$<$13m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$14m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$15m  &137.793  &119.965  &119.459  &119.077  &118.783  &118.236 \\
			R$<$16m  &155.092  &123.854  &122.026  &120.799  &119.983  &118.711 \\
			R$<$17m  &163.580  &126.425  &123.686  &121.880  &120.718  &119.023 \\

@@

		\section{Conclusion}
		The total events rate from physical channel excepting supernova event in JUNO is less 
		than 1 Hz. So the data volume of physical events excepting supernova event is negligible 
		comparing with those from radioactity backgrounds. With
		a typical energy threshold 0.5MeV , the data volume of radioactity
		backgrounds is about ??? MBytes/s. The data volume of muon events is about 100MBytes/s.

		With a more sophisticated trigger scheme, the energy threshold can be reduced to 0.2MeV which 
		is preferred by solar neutrinos and supernova neutrinos study. With 0.2MeV energy threshold and
		17m radius threshold the data volume of radioactity backgrounds is about ??? MBytes/s. Table.6
		show the data volume of central detector radioactivity events on different energy and radius 
		threshold.

>>>>

		\section{Estimation of data volume in JUNO}
		JUNO is proposed to run at least 6 years for neutrino mass hiarachy measurements and other physics topics. 
		It's important for offline data processing and disk storage preparation to estimate the data volume after 6 years running. 
		Different events have different event size, depending on number of photo-electrons detected by CD.
		The data volume of physical events excepting muon events and supernova events can be negligible comparing with radioactivity events. 
		Fig.5  shows the fired PMT number distributions from different radioactivity events on each detector material with 300ns trigger time window.

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{distribution_of_fired_PMTNum.eps}
			\figcaption{\label{fig2}   Distributions of fired PMT number on different materials with 300ns trigger time window}
		\end{center}

@@

		In JUNO electronic system for low energy radioactivity events the assuming sampling time window is 1 $\mu$s. Each sampling point contribute 2 bytes data, so each fired PMT contribute 2 KBytes data. The estimated data volume about radioactivity events of CD on different energy and radius threshold is listed in table 6.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The data volume of central detector radioactivity events on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  disk storage space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline

			R$<$10m  &439.131   &141.307  &127.054  &125.725  &123.941  &122.329 \\  
			R$<$11m  &508.392   &143.338  &128.081  &126.514  &124.518  &122.521 \\
			R$<$12m  &786.779   &151.416  &132.214  &129.729  &126.891  &123.280 \\
			R$<$13m  &1090.13   &158.894  &136.093  &132.778  &129.154  &123.988 \\
			R$<$14m  &1090.13   &158.894  &136.093  &132.778  &129.154  &123.988 \\
			R$<$15m  &1332.45   &176.623  &143.929  &138.059  &132.638  &125.636 \\
			R$<$16m  &2351.66   &268.445  &183.459  &163.936  &149.375  &134.092 \\
			R$<$17m  &2851.79   &329.130  &209.007  &180.195  &159.631  &139.657 \\

@@

		\section{Conclusion}
		The total events rate from physical channel excepting supernova event in JUNO is less 
		than 1 Hz. So the data volume of physical events excepting supernova event is negligible 
		comparing with those from radioactity backgrounds. With
		a typical energy threshold 0.5MeV , the data volume of radioactity
		backgrounds is about 210 MBytes/s. The data volume of muon events is about 100MBytes/s.

		With a more sophisticated trigger scheme, the energy threshold can be reduced to 0.2MeV which 
		is preferred by solar neutrinos and supernova neutrinos study. With 0.2MeV energy threshold and
		17m radius threshold the data volume of radioactity backgrounds is about 329 MBytes/s. Table.6
		show the data volume of central detector radioactivity events on different energy and radius 
		threshold.
